Appendix 2: Density dependence

### 2021-02-19 analysis/supplementary-materials/appendix_density_dependence.Rmd
Created appendix for SPEI data
sentence wrap.

---
title: "Density dependence"
author: "Eric R. Scott"
date: '2020-09-13'
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/ecology.csl" # Insert path for the bib-style
---

@@

>>>>

---
title: "Appendix 2: Density dependence"
author: "Eric R. Scott"
date: '2020-09-13'
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/ecology.csl" # Insert path for the bib-style
editor_options:
  markdown:
    wrap: sentence
---

@@

-   Use a tensor product with a monotonically decreasing P-spline for the distance dimension (see Wood book 5.3.6, something like `ssp <- s(x, bs = "ps", k = k); ssp$mono <- -1`
